A generalization of the Bradley-Terry model for draws in chess

### 2020-09-15 inst/jebo_chess_revision2.tex
much better phrasing

Grandmasters Anand, Karpov, and Kasparov have a long-standing rivalry
and have played many games amongst themselves.  A summary may be found
in Table~\ref{kka}, \textcolor{red}{showing games played from 1981 to
  2017.  During this time, the players' strengths might have changed
  substantially.  Statistical assessment of time-varying strength is
  possible with the reified entity technique and this is discussed
  under further work below.  However, we may adopt one of two
  approaches: either we make the working assumption that the strengths
  do not change, or alternatively we wish to make inferences about the
  players' strength {\em averaged over a playing career}.  Either
  way,} Equation~\ref{likelihood_WD} becomes

>>>>

Grandmasters Anand, Karpov, and Kasparov have a long-standing rivalry
and have played many games amongst themselves.  A summary may be found
in Table~\ref{kka}, \textcolor{red}{showing games played from 1981 to
  2017.  During this time, the players' strengths might have changed
  substantially.  Statistical assessment of time-varying strength is
  possible with the reified entity technique and this is discussed
  under further work below.  However, we may treat the strengths as
  constant by adopting one of two approaches: either we assume that
  the strengths do not change, or alternatively we interpret the
  strengths as measures of ability {\em averaged over a playing
    career}.  Either way,} Equation~\ref{likelihood_WD} becomes
